Introduction to\\ Swedish Civil Contingencies Agency (MSB) methodological support for introducing \acp{isms}.

### 2017-04-03 msbframework/msbintro/msbintro.tex
Missed to translate one slide.

\begin{frame}{ISO 27000}
  \begin{itemize}
    \item Inte bara myndigheter som kan ha nytta av detta.

    \item Finns möjlighet för certifiering av ISO 27000 för alla 
      organisationer.

    \item MSB:s metodstöd är alltså anpassat efter dessa internationella 
      standarder.

>>>>

\begin{frame}{ISO 27000}
  \begin{itemize}
    \item This is not just for governmental agencies.

    \item Any organisation can certify themselves for ISO27000

    \item MSB:s methodological support is adapted to the international
      standards.
